%-----------------------------------------------------------------------------%
\chapter*{Acknowledgments}
%-----------------------------------------------------------------------------%

First and foremost, I would like to thank Allah SWT and His prophet Muhammad SAW.
I am grateful for the good health and wellbeing that allows me to complete this thesis.
In writing this thesis, I was given help by a lot of people.
I would like to personally thank all these people:

\begin{enumerate}
    \item My parents, Brilliantoro and Maulina Dian Purwanti and my siblings, for their endless love and support.
    \item \pembimbing~ as one of my supervisor for his generosity and helpful advices, and for giving me the opportunity of doing my thesis here in TU Dresden.
    \item \pembimbingDua~ as my other supervisor also for his many helpful advices and discussions, and his plentiful tips and kind invitation to allow us enjoy our visit in Dresden.
    \item My academic advisor, Siti Aminah, S.Kom., M.Kom. for providing guidance through these four years in Universitas Indonesia.
    \item Muhammad Ayaz Dzulfikar, for accompanying me through my daily life surviving in Dresden.
    \item Faridah Nur Suci Amirahmandani, for her continuous support in writing this thesis.
    \item My friends from Ristek, Capung, \emph{Kroco} and many other people who supported me these four years, that I cannot mention here individually.
\end{enumerate}

\vspace*{0.1cm}
\begin{flushright}
Dresden, 14 June 2019\\[0.1cm]
\vspace*{1cm}
\penulis

\end{flushright}